---
title: "BSMM_lab_2"
subtitle: "BSMM 8740 Fall 2023"
author: "Nishanth Prasad Edakkattil "
date: "September 25"
format: html
editor: visual
self-contained: true
---

## Setup

```{r}
install.packages("magrittr")
install.packages("tidyverse")
install.packages("tidymodels")
install.packages("gt")
install.packages("gtExtras")
install.packages("DataExplorer")

```

```{r}
library(magrittr)     # the pipe
library(tidyverse)    # for data wrangling + visualization
library(tidymodels)   # for modeling
library(gt)           # for making display tables
library(gtExtras)     # helper functions for beautiful tables
library(DataExplorer) #
```

Load packages and data:

```{r load-pkg-data}
#| message: false
the_tate <- readr::read_delim("data/the-tate-collection.csv", ";", escape_double = FALSE, trim_ws = TRUE)
the_tate_artists <- readr::read_csv("data/the-tate-artists.csv")

```

## Exercises

```{r}
view(the_tate)
```

```{r}
view(the_tate_artists)
```

### Exercise 1

```{r}
the_tate %>% dplyr::summarize(
  unique.length= unique(artistId),
  min_year= min(year,na.rm=TRUE),
  max_year=max(year,na.rm= TRUE),
  min_acquisitionYear= min(acquisitionYear,na.rm=TRUE),
  max_acquisitionYear= max(acquisitionYear,na.rm=TRUE)
)
```

The `the_tate` dataset has 3342 unique artists who worked from 1545 to 2012. The works were acquired between the years 1823 and 2013.

```{r}
DataExplorer::introduce(the_tate)
DataExplorer::plot_missing(the_tate)
```

### Exercise 2

```{r}
missing_dates<- sum(is.na(the_tate$year))
print(missing_dates)
```

```{r}

library(dplyr)
library(tibble)
#Displaying the missing works for each artist
artist_missing_works <- the_tate %>%
  group_by(artist) %>%
  summarize(Missing_Works = sum(is.na(year))) %>%
  filter(Missing_Works > 0) %>%
  arrange(desc(Missing_Works))
print(artist_missing_works)
#Finding the no of artists
artist_missing_works <- artist_missing_works %>% dplyr::mutate(pct_missing_years = (Missing_Works/sum(Missing_Works))*100,cumsum(pct_missing_years))
count(artist_missing_works)



```

How many number of works with missing dates is 5397.

The number of artists whose works have missing dates is 461

It would require resolving missing year data for only 11 artists resolve resolve at least 50% of the missing data.

The missing year data likely to be classified as MAR.

### Exercise 3

```{r}
artist_works <- the_tate %>% dplyr::group_by(artistId) %>% dplyr::summarize(
  number_of_works = n()
) %>% dplyr::arrange(desc(number_of_works))

artist_works <- artist_works %>% dplyr::mutate(pct_of_work = (number_of_works/sum(number_of_works))*100)

artist_works %>% gt() %>% 
  gt_theme_538() 

the_tate %>% dplyr::filter(artistId %in% c(558,2121)) %>% dplyr::select(artistId,artist) %>% distinct(artistId,artist) 
```

The artist with the most works in the Tate collection is Turner, Joseph Mallord William having artist ID 558.

The artist with the tenth-most works in the Tate collection is Warhol, Andy having artistID = 2121.

### Exercise 4

The artist with the greatest number of works in the Tate collection represent 56.919697692% of the total number of works

### Exercise 5

```{r}
total_artist_title_pairs <- the_tate %>% dplyr::select(artistId , title) %>% tibble::as_tibble() %>% count()
total_artist_title_pairs_distinct <- the_tate %>% dplyr::select(artistId , title) %>% dplyr::distinct() %>% count()
#showing the total number of rows
print(total_artist_title_pairs)
#showing the total number of distinct rows
print(total_artist_title_pairs_distinct)
#showing the total number of duplicate rows.
print(total_artist_title_pairs-total_artist_title_pairs_distinct)
```

There are 23705 duplicate artist-title pairs

### Exercise 6

```{r}
the_tate_area <- the_tate %>% dplyr::select(artist,artistId,width,height) %>% dplyr::mutate(area = (width*height)/10000) %>% tidyr::drop_na(area) %>% dplyr::arrange(desc(area))

dplyr::slice_head(the_tate_area)
dplyr::slice_tail(the_tate_area)
```

The artist with the largest work in the tate collection is Therrien, Robert

The artist with the smallest work in the collection is Mesens, E.L.T.. The smallest work has area 0.0237 $\text{cm}^2$

### Exercise 7

...

```{r}
#Joining the tables
joined_data <- the_tate %>% dplyr::left_join(the_tate_artists, by = join_by(artistId == id)) %>% tidyr::drop_na(gender)

joined_data <- joined_data  %>% dplyr::group_by(gender)

view(joined_data)
```

### Exercise 8

The annual return in the SPX price in 2020 was \_\_\_%.

The corresponding price volatility was \_\_\_%.

### Exercise 9

The period volatility was \_\_\_.\_%

### 
